BExIS Manual for Traitdata

### 2018-02-14 bexis_handbook/bexis_handbook_traits.Rmd
complete bexis handbook, first draft

---
title: "BExIS Manual for Traitdata"
author: "Florian D. Schneider"
date: "13 February 2018"
output:  pdf_document
bibliography: ../manuscript/div05.bib
csl: ../manuscript/amnat.csl
---

Functional traits have become a core concept of ecological research and have been assessed for many organism groups within the Biodiversity Exploratories project.

@@

- The `occurrence` extension (https://ecologicaltraitdata.github.io/ETS/#extension-occurrence) contains vocabulary to describe information on the level of individual specimens, such as sex, life stage or age. This also includes the method of sampling and preservation, as well as date and geographical location, which provides an important resource to analyse trait variation due to differences in space and time.
- The `measurementOrFact` extension (https://ecologicaltraitdata.github.io/ETS/#extension-measurement-or-fact) provides terms to describe information at the level of single measurements or reported facts, such as the original literature from where the value is cited, the method of measurement or statistical method of aggregation. It provides important information that allows for the tracking of potential sources of noise or bias in measured data (e.g. variation in measurement method) or aggregated values (e.g. statistical method applied), as well as the source of reported facts (e.g. literature source or expert reference).   
- The `BiodiversityExploratories` extension provides terms to relate the trait measurement to plots and sites in the exploratories framework, including `ExploratoriesPlotID`, `Exploratory` and `ExploType`

@@

When saving your data, it is recommended to use

>>>>

---
title: "BExIS Manual for Traitdata"
author: "Florian D. Schneider"
date: "13 February 2018"
output:  
  pdf_document:
    includes:
      in_header: header.tex
    toc: yes
fontsize: 10pt
geometry: margin=1.5in
bibliography: ../manuscript/div05.bib
csl: ../manuscript/amnat.csl
---

# Ecological Traits

Ecological traits have become a core concept of ecological research and have been assessed for many organism groups within the Biodiversity Exploratories project.

@@

- The `occurrence` extension (https://ecologicaltraitdata.github.io/ETS/#extension-occurrence) contains vocabulary to describe information on the level of individual specimens, such as sex, life stage or age. This also includes the method of sampling and preservation, as well as date and geographical location, which provides an important resource to analyse trait variation due to differences in space and time.
- The `measurementOrFact` extension (https://ecologicaltraitdata.github.io/ETS/#extension-measurement-or-fact) provides terms to describe information at the level of single measurements or reported facts, such as the original literature from where the value is cited, the method of measurement or statistical method of aggregation. It provides important information that allows for the tracking of potential sources of noise or bias in measured data (e.g. variation in measurement method) or aggregated values (e.g. statistical method applied), as well as the source of reported facts (e.g. literature source or expert reference).
- The `BiodiversityExploratories` extension  (http://ecologicaltraitdata.github.io/ETS/#extension-biodiversity-exploratories)  provides terms to relate the trait measurement to plots and sites in the exploratories framework, including `ExploratoriesPlotID`, `Exploratory` and `ExploType`

@@

For saving your data for upload in BExIS, you would use

```
write.csv(datasetStd, file = "filename.csv", row.names = FALSE)
```

which and omits the row names when produces a comma separated file with points as decimal delimiter.
